### 2014-10-06 Projects/NFRL_Emissions/Report/ECS_Testing.tex
NFRL_Emissions: rename directory

\hypersetup{
  pdftitle={Design Fires for Emission Control System Commissioning},
  pdfauthor={Weinschenk, Craig G and Bundy, Matt}, 
  pdfsubject={} 
  }

@@

\headerC{
\flushright{
Craig G. Weinschenk \\
Matt Bundy \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\begin{table}
\centering
\caption{Design fires for ECS commissioning tests}
\label{tab:fires}
\vskip.5\baselineskip
\begin{tabular}{ccccc}
\hline \hline
Test ID & Fuel & Peak HRR (MW) & Burn Time (min) & Test Goal  \\
\hline \hline
1-3  & Natural Gas  & 2-8   & 60  & Temperature  \\
4  & Wood w/ PVC  & $\approx$ 1.5-2 & $\approx$ 50  & Acid, Train 3 \\
5  & Group A Comm. & $\approx$ 3 & $\approx$ 20  & Soot, Train 3 \\
6  & Wood w/ PVC  & $\approx$ 1.5-2 & $\approx$ 50  & Acid, Train 4 \\
7  & Group A Comm. & $\approx$ 3 & $\approx$ 20  & Soot, Train 4 \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}
\centering
\caption{Mass flow rate of natural gas for experimental range of HRRs}
\label{tab:ng_flow}
\vskip.5\baselineskip
\begin{tabular}{cc}
\hline \hline
Fire Size (MW) & Flow Rate (kg/s)  \\
\hline \hline
2  &  0.04 \\
4  &  0.08 \\
6  &  0.12 \\
8  &  0.16 \\
\hline
\end{tabular}
\end{table}

@@

\begin{multline}
\C_2\H_3\Cl \,+\, 7.29(0.21 \O_2 \,+\, 0.79 \N_2) \\
\rightarrow 9.76(0.102\HCl \,+\, 0.103\H_2\O \,+\, 0.014 \C\O \,+\, 0.098 \C\O_2 \,+\, 0.092 \C \,+\, 0.59 \N_2)
\label{eq:hcl_reac}
\end{multline}
Based on Eq.~(\ref{eq:hcl_reac}), there is a 58 \% mass basis theoretical yield of HCl (\ref{app:crib}).  Experimental data based on burning PVC over a wide range of test conditions and using a wide range of measurement techniques puts the HCl yield between 10 and 56 \% \cite{Leeds:PVC}. Using data for a similarly scaled and ventilated test, the estimated HCl yield is 32 \% \cite{Persson1998}. Since each crib contains 3.63 kg of PVC and the test calls for 4 cribs, the expected yield of HCl at the source fire is 4.65 kg (10.2 lb). Based on an estimated {\bf 60-70} \% loss of HCl to gas phase conversion and reaction through the duct work, the estimated mass of HCL upstream of the scrubber is {\bf 1.4-1.9} kg ({\bf 3-4} lb).

@@

\begin{figure}[h!]
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\includegraphics[width=0.45\textwidth]{../Figures/comm_ignite} &
\includegraphics[width=0.45\textwidth]{../Figures/comm_burn} \\
\end{tabular*}
\caption{Two stacks of 3 boxes of group A commodities just after ignition (left) and fully involved (right). The boxes are lit with shredded paper and an electric match.  Peak heat release is $\approx$ 2.5 MW.}
\label{fig:comm_burn}
\end{figure}

@@

\chapter{Experimental Test Procedures}
\label{test_procedure}
\subsection{Test 1 Procedure}
\label{procedure1}

@@

\subsection{Test 2 Procedure}
\label{procedure2}
\begin{enumerate}
  \item All flammable liquid stored are in outdoor containment building with a fuel spill containment floor. 
  \item A secondary containment device (graduate cylinder) will be used when transferring fuels and conducting fire tests.
  \item Position wood cribs on cement board.
  \item Fill 3 ignition pans with 500 mL heptane.
  \item Slide each pan of heptane under one of three wood cribs. 
  \item Ignite fuel pans with a 1.83 m (6 ft) propane wand ignitor.
  \item Verify all post fire materials are sufficiently cool to prevent smoldering or off gassing.
  \item Workers are required to use PPE when performing post-fire cleanup.

@@

\subsection{Test 3 Procedure}
\label{procedure3}
\begin{enumerate}
  \item Position commodity boxes on cement board.
  \item Position shredded paper ignition source in 0.15 m gap between stacked boxes.
  \item Ignite shredded paper with 1.83 (6 ft) propane wand ignitor.
  \item Verify all post fire materials are sufficiently cool to prevent smoldering or off gassing.
  \item Workers are required to use PPE when performing post-fire cleanup.
\end{enumerate}

\chapter{Results}
Seven tests were conducted to commission the NFRL ECS:
\begin{enumerate}
\item 4 MW natural gas burn, exhaust train 3
\item 4 MW natural gas burn, exhaust train 4
\item 8 MW natural gas burn, exhaust trains 3 and 4
\item Wood crib burn, ECS train 3
\item Commodity burn, ECS train 3
\item Wood crib burn, ECS train 4
\item Commodity burn, ECS train 4
\end{enumerate}
Emission measurements were not made for tests 1, 2, and 3 since they were natural gas tests. Measurements were made during tests 4, 5, 6 and 7. The measurements were taken at the exhaust stack; the farthest downstream sensor port in the ECS.  Data was recorded throughout the duration of the experiments and then time averaged. The  Table~\ref{tab:hcl_data} shows the results including the mean mass flow rate of HCl for tests 4 and 6 as well as from a similar test conducted in 2001.

\begin{table}[h]
\centering
\caption{Exhaust measurements for wood crib experiments}
\label{tab:hcl_data}
\vskip.5\baselineskip
\begin{tabular}{cccc}
\hline \hline
Measurement Quantity & Test 4 & Test 6 & 2001 Test  \\
\hline \hline
Metered Volume (dcf)           &  47.39  &  59.22  &  36.52  \\
Total Test Time (min)          &  56.1   &  68.3   &  60     \\
Gas Temperature ($^{\circ}$F)  &  285    &  296    &  268    \\
Oxygen (\%)                    &  19.16  &  19.56  &  19.7   \\
Carbon Dioxide (\%)            &  0.81   &  1.00   &  1.1    \\
Velocity (ft/s)                &  54.37  &  54.36  &  45.09  \\
HCl Concentration (ppmdv)      &  8.60   &  10.55  &  2.98   \\
Mass Rate (lb/hr)              &  2.96   &  3.57   &  0.86   \\
\hline
\end{tabular}
\end{table}

Table~\ref{tab:hcl_data} shows the results including particulate emissions for tests 5 and 7.

\begin{table}[h]
\centering
\caption{Exhaust measurements for commodity experiments}
\label{tab:hcl_data}
\vskip.5\baselineskip
\begin{tabular}{ccc}
\hline \hline
Measurement Quantity & Test 5 & Test 7  \\
\hline \hline
Metered Volume (dcf)                &  40.97  &  38.28  \\
Total Test Time (min)               &  48.1   &  43     \\
Gas Temperature ($^{\circ}$F)       &  288    &  300    \\
Oxygen (\%)                         &  18.92  &  19.36  \\
Carbon Dioxide (\%)                 &  0.99   &  0.91   \\
Velocity (ft/s)                     &  53.75  &  55.18  \\
Particulate Concentration (g/dscf)  &  $< 4.67\text{\sc{e}-}5$   &  $< 5.08 \text{\sc{e}-}5$  \\
Mass Rate (lb/hr)                   &  $<$ 0.37   &  $<$ 0.40   \\
\hline
\end{tabular}
\end{table}

@@

\appendix
\section{Schematics of the National Fire Research Lab}
\label{app:nfrl_images}
Images to describe the layout of the existing and additional lab space.

\begin{figure}[h!]
\includegraphics[width=\textwidth]{../Figures/plan_view2}
\caption {Plan view of the NFRL indicating location of ECS test fires.}
\label{fig:NFRL_plan}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{../Figures/section_2}
\caption {Rendering of the NFRL showing the original lab space (left) and the new lab space (right).}
\label{fig:NFRL_render}
\end{figure}
\end{document}

>>>>

\hypersetup{
  pdftitle={Design Fires for Emission Control System Commissioning},
  pdfauthor={Weinschenk, Craig G and Bundy, Matthew}, 
  pdfsubject={} 
  }

@@

\headerC{
\flushright{
Craig G. Weinschenk \\
Matthew Bundy \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\begin{table}
\centering
\caption{Design fires for ECS commissioning tests}
\label{tab:fires}
\begin{tabular}{ccccc}
\toprule[1.5pt]
Test ID & Fuel & Peak HRR (MW) & Burn Time (min) & Test Goal  \\
\midrule
1-3  & Natural Gas  & 2-8   & 60  & Temperature  \\
4  & Wood w/ PVC  & $\approx$ 1.5-2 & $\approx$ 50  & Acid, Train 3 \\
5  & Group A Comm. & $\approx$ 3 & $\approx$ 20  & Soot, Train 3 \\
6  & Wood w/ PVC  & $\approx$ 1.5-2 & $\approx$ 50  & Acid, Train 4 \\
7  & Group A Comm. & $\approx$ 3 & $\approx$ 20  & Soot, Train 4 \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

\begin{table}
\centering
\caption{Mass flow rate of natural gas for experimental range of HRRs}
\label{tab:ng_flow}
\begin{tabular}{cc}
\toprule[1.5pt]
Fire Size (MW) & Flow Rate (kg/s)  \\
\midrule
2  &  0.04 \\
4  &  0.08 \\
6  &  0.12 \\
8  &  0.16 \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

\begin{multline}
\C_2\H_3\Cl \,+\, 7.29(0.21 \O_2 \,+\, 0.79 \N_2) \\
\rightarrow 9.76(0.102\HCl \,+\, 0.103\H_2\O \,+\, 0.014 \C\O \,+\, 0.098 \C\O_2 \,+\, 0.092 \C \,+\, 0.59 \N_2)
\label{eq:hcl_reac}
\end{multline}
Based on Eq.~(\ref{eq:hcl_reac}), there is a 58 \% mass basis theoretical yield of HCl (\ref{app:crib}).  Experimental data based on burning PVC over a wide range of test conditions and using a wide range of measurement techniques puts the HCl yield between 10 and 56 \% \cite{Leeds:PVC}. Using data for a similarly scaled and ventilated test, the estimated HCl yield is 32 \% \cite{Persson1998}. Since each crib contains 3.63 kg of PVC and the test calls for 4 cribs, the expected yield of HCl at the source fire is 4.65 kg (10.2 lb). Based on an estimated 60-70 \% loss of HCl to gas phase conversion and reaction through the duct work, the estimated mass of HCL upstream of the scrubber is 1.4-1.9 kg (3-4 lb).

@@

\begin{figure}[!ht]
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\includegraphics[width=0.45\textwidth]{../Figures/comm_ignite} &
\includegraphics[width=0.45\textwidth]{../Figures/comm_burn} \\
\end{tabular*}
\caption{Two stacks of 3 boxes of group A commodities just after ignition (left) and fully involved (right). The boxes are lit with shredded paper and an electric match.  Peak heat release is $\approx$ 2.5 MW.}
\label{fig:comm_burn}
\end{figure}

@@

\chapter{Experimental Test Procedures}
\label{test_procedure}
\section{Test 1 Procedure}
\label{procedure1}

@@

\section{Test 2 Procedure}
\label{procedure2}
\begin{enumerate}
  \item All flammable liquid stored are in outdoor containment building with a fuel spill containment floor. 
  \item A secondary containment device (graduate cylinder) will be used when transferring fuels and conducting fire tests.
  \item Position wood cribs on cement board.
  \item Fill 3 ignition pans with 500 mL heptane.
  \item Slide each pan of heptane under one of three wood cribs. 
  \item Ignite fuel pans with a 1.83 m (6 ft) propane wand ignitor.
  \item Verify all post fire materials are sufficiently cool to prevent smoldering or off gassing.
  \item Workers are required to use PPE when performing post-fire cleanup.

@@

\section{Test 3 Procedure}
\label{procedure3}
\begin{enumerate}
  \item Position commodity boxes on cement board.
  \item Position shredded paper ignition source in 0.15 m gap between stacked boxes.
  \item Ignite shredded paper with 1.83 (6 ft) propane wand ignitor.
  \item Verify all post fire materials are sufficiently cool to prevent smoldering or off gassing.
  \item Workers are required to use PPE when performing post-fire cleanup.
\end{enumerate}

\chapter{Results}
Seven tests were conducted to commission the NFRL ECS:
\begin{enumerate}
\item 4 MW natural gas burn, exhaust train 3
\item 4 MW natural gas burn, exhaust train 4
\item 8 MW natural gas burn, exhaust trains 3 and 4
\item Wood crib burn, ECS train 3
\item Commodity burn, ECS train 3
\item Wood crib burn, ECS train 4
\item Commodity burn, ECS train 4
\end{enumerate}
Emission measurements were not made for tests 1, 2, and 3 since they were natural gas tests. Measurements were made during tests 4, 5, 6 and 7. The measurements were taken at the exhaust stack; the farthest downstream sensor port in the ECS.  Data was recorded throughout the duration of the experiments and then time averaged. Table~\ref{tab:hcl_data} shows the results including the mean mass flow rate of HCl for tests 4 and 6 as well as from a similar test conducted in 2001.

\begin{table}[!ht]
\centering
\caption{Exhaust measurements for wood crib experiments}
\label{tab:hcl_data}
\begin{tabular}{cccc}
\toprule[1.25pt]
Measurement Quantity & Test 4 & Test 6 & 2001 Test  \\
\midrule
Metered Volume (dcf)           &  47.39  &  59.22  &  36.52  \\
Total Test Time (min)          &  56.1   &  68.3   &  60     \\
Gas Temperature ($^{\circ}$F)  &  285    &  296    &  268    \\
Oxygen (\%)                    &  19.16  &  19.56  &  19.7   \\
Carbon Dioxide (\%)            &  0.81   &  1.00   &  1.1    \\
Velocity (ft/s)                &  54.37  &  54.36  &  45.09  \\
HCl Concentration (ppmdv)      &  8.60   &  10.55  &  2.98   \\
Mass Rate (lb/hr)              &  2.96   &  3.57   &  0.86   \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

Table~\ref{tab:part_data} shows the results including particulate emissions for tests 5 and 7.

\begin{table}[!ht]
\centering
\caption{Exhaust measurements for commodity experiments}
\label{tab:part_data}
\begin{tabular}{ccc}
\toprule[1.25pt]
Measurement Quantity & Test 5 & Test 7  \\
\midrule
Metered Volume (dcf)                &  40.97  &  38.28  \\
Total Test Time (min)               &  48.1   &  43     \\
Gas Temperature ($^{\circ}$F)       &  288    &  300    \\
Oxygen (\%)                         &  18.92  &  19.36  \\
Carbon Dioxide (\%)                 &  0.99   &  0.91   \\
Velocity (ft/s)                     &  53.75  &  55.18  \\
Particulate Concentration (g/dscf)  &  $< 4.67\text{\sc{e}-}5$   &  $< 5.08 \text{\sc{e}-}5$  \\
Mass Rate (lb/hr)                   &  $<$ 0.37   &  $<$ 0.40   \\
\bottomrule[1.25pt]
\end{tabular}
\end{table}

@@

\appendix
\chapter{Schematics of the National Fire Research Lab}
\label{app:nfrl_images}
\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../Figures/plan_view2}
\caption {Plan view of the NFRL indicating location of ECS test fires.}
\label{fig:NFRL_plan}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../Figures/section_2}
\caption {Rendering of the NFRL showing the original lab space (left) and the new lab space (right).}
\label{fig:NFRL_render}
\end{figure}
\end{document}
